---
title: 'Module 1: Fun with Matrices'
author: "Robetauli Simangunsong"
date: "Oct 08 2021"
output:
  html_document:
    df_print: paged
---
```{r include = FALSE}
knitr::opts_chunk$set(out.height = "\\textheight",  out.width = "\\textwidth")
```

# Part 1 Matrix operations

Let's review some basic matrix operations.
First build the following  3 x 3 matrix 
$\mathbf{X} = \begin{bmatrix} 1 & 2 & 3\\4&5&6 \\7&8&9 \end{bmatrix}$

by completing this code:
```r
  mat_vals <- seq()
  X <- matrix(mat_vals, nrow=)
```

Put you code here, and print out your matrix to make sure you got it right!
```{r}
matrix(1:9, nrow=3, ncol=3)
X <- matrix(1:9, nrow=3, ncol=3)
```


Add $\mathbf{X}$ to $\mathbf{Y}$ and store it as $\mathbf{Z1}$. 
```{r}
Y <- 10:18
dim(Y) <- c(3,3)
Y <- 10:18 
dim(Y)<- c(3,3)
Y <- matrix (10:18, nrow=3, ncol=3)
dim(Y) <- c(3,3)
Z1 <- dim(Y)
```

Add $\mathbf{Y}$ to $\mathbf{X}$ and store it as $\mathbf{Z2}$.
```{r}
dim(X) <- c(3,3)
Z2 <- dim(X)
```

Use the identical() function to test if $\mathbf{Z1} = \mathbf{Z2}$ 
```{r}
identical(Z1,Z2)

```


**What does this demonstrate about matrix addition?** It demonstrates the two objects are equal because the result is true

Now lets try matrix multiplication using the operator
```r 
%*%
``` 
Matrix multiple $\mathbf{Y}\mathbf{X}$ and store it as a variable named YX
```{r}
Y%*%X
YX <- Y%*%X
```

Multiply $\mathbf{X}\mathbf{Y}$ and store it as a variable name XY
```{r}
X%*%Y
XY <- X%*%Y
```


**Are these matrices the same? False. What does this demonstrate? ** It demonstrates the two objects are not equal
```{r}
identical(YX,XY)

```


Make a 3 x 3 identity matrix ($\mathbf{I}$) using the diag() function and store it as variable I
```{r}
diag(19:27, nrow=3, ncol=3)
I <-diag(19:27, nrow=3, ncol=3)
```


Matrix multiply  $\mathbf{I}$ by $\mathbf{X}$
```{r}
I %*% X

```


Let's try multiplying $\mathbf{X}$ by a new matrix, $\mathbf{B}$, and also
try adding $\mathbf{X}$ and  $\mathbf{B}$ below **Note: This will not work.**
Change the code that creates $\mathbf{B}$, so that both addition and 
multiplication work.

```{r}
B <- matrix(c(1,2,2,1), nrow=2)


```


**What error messages did you get when trying these operations? Error in X %*% B : non-conformable arguments What do the messages mean? It means X%*%B is not the same as I%*%X
and how did you fix $\mathbf{B}$ so that the operations worked?**
matrix (c(1,22,1,2,1,1,2,2), nrow=3)
C <- matrix(c(1,2,2,1,2,1,1,2,2), nrow=3)
X%*%C















